Behavior Driven Development in Haskell

### 2012-05-30 paper.tex
Grammar

The word ``behavior'' is associated with imperative actions.
Since pure functions of Haskell are static,
this word might be improper for Haskell.
However, this word is already used in Haskell community~\cite{typeclassopedia}.
So, we use ``behavior'' instead of defining a new terminology in this paper.

>>>>

The word ``behavior'' is associated with imperative actions.  Since
pure functions of Haskell are static, this word might be improper for
Haskell.  However, this word is already used in the Haskell
community~\cite{typeclassopedia}.  So, we use ``behavior'' instead of
defining terminology in this paper.
